---
title: "AI Advice – Pretest Analysis"
subtitle: "Evaluation of AI justifications"
author: "Ceren Ay"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    code-tools: true
    embed-resources: true
    df-print: kable
execute:
  warning: false
  message: false
params:
  data_dir: "../pretest"          
  exclude_failed_checks: true     
  speeder_cutoff: 0.33           
  exclude_speeders: false         
  save_outputs: true              
---

## About this document

NOTE: Used Claude Cowork a bit in this file to organize the results and visualize better(can be discussed how well it worked).

This file analyses the **pretest** of the AI-advice experiment. After reading the
allocation task (dictator game with a taking option: decision-maker has £10,
recipient has £4), participants saw three AI responses that all recommend
*"give £3 to the recipient"* but differ in the **evaluative standard** and
justification:

| Condition | Evaluative standard | Justification (short) |
|---|---|---|
| `equal` | Equality | Both end up with £7; upholds the principle of equality |
| `fair` | Fairness | Both end up with £7; aligns with the principle of fairness |
| `fairequal` | Fairness and Equality | Both end up with £7; promotes fairness and equality |

Each response was rated (within subjects, block order randomised by Qualtrics) on
three 5-point Likert items (1 = Strongly disagree … 5 = Strongly agree):

1. **Standard matters** – "The recommendation is based on a standard that matters to me"
2. **Reasoning makes sense** – "The reasoning behind this recommendation makes sense to me"
3. **Inclined to revise** – "After reading this response, I feel more inclined to revise my allocation decision"


```{r}
#| label: setup
#| code-fold: false

required <- c("tidyverse", "lme4", "lmerTest", "emmeans", "ordinal", "knitr")
missing  <- required[!vapply(required, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing)) stop("Please install: ", paste(missing, collapse = ", "),
                          "\n  install.packages(c(\"", paste(missing, collapse = "\", \""), "\"))")

suppressPackageStartupMessages({
  library(tidyverse)
  library(lme4)
  library(lmerTest)
  library(emmeans)
  library(knitr)
})

# ---- Labels (edit here if conditions/items change) -------------------------
advice_labels <- c(
  equal     = "Equality",
  fair      = "Fairness",
  fairequal = "Fairness & Equality"
)
item_labels <- c(
  "1" = "Standard matters",
  "2" = "Reasoning makes sense",
  "3" = "Inclined to revise"
)
likert_levels <- c("Strongly disagree", "Somewhat disagree",
                   "Neither agree nor disagree", "Somewhat agree", "Strongly agree")

# Qualtrics block IDs of the randomised advice blocks (used only if the
# randomisation order is exported, see the "Order effects" section)
block_to_advice <- c(
  "BL_3Vona5LNo1cvl0q" = "equal",     "AI advice 1" = "equal",
  "BL_7QbYfICheXo8su2" = "fair",      "AI advice 2" = "fair",
  "BL_3xC1DEX1CbvBK62" = "fairequal", "AI advice 3" = "fairequal"
)

# Correct answers of the comprehension checks (amount in £)
correct_q5 <- 4   # Q5: most you can take
correct_q6 <- 0   # Q6: least you can give

# ---- Plot style -------------------------------------------------------------
pal_advice <- c("#2a78d6", "#eb6834", "#1baf7a")          # fixed categorical order
pal_likert <- c("#c73a39", "#f0a19e", "#cfcdc8", "#8db6ea", "#2a78d6")  # diverging, gray midpoint
names(pal_likert) <- likert_levels

theme_set(
  theme_minimal(base_size = 12) +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.y = element_line(colour = "grey90", linewidth = 0.3),
          panel.grid.major.x = element_blank(),
          strip.text = element_text(face = "bold", hjust = 0),
          legend.position = "bottom",
          plot.title.position = "plot")
)

if (params$save_outputs) dir.create("output", showWarnings = FALSE)
```

## Data import

```{r}
#| label: import

read_qualtrics <- function(path) {
  hdr <- names(read_csv(path, n_max = 0, show_col_types = FALSE))
  dat <- read_csv(path, col_names = hdr, skip = 1, col_types = cols(.default = "c"),
                  show_col_types = FALSE)
  # Drop Qualtrics' extra header rows (question text + ImportId rows)
  dat <- dat |>
    filter(!(StartDate %in% c("Start Date", "StartDate")),
           !str_detect(StartDate, fixed("ImportId")))
  # Clean names: Qualtrics adds spaces, e.g. "advice_equal _1" -> "advice_equal_1"
  names(dat) <- str_replace_all(names(dat), "\\s+", "")
  dat |> mutate(source_file = basename(path))
}

files <- list.files(params$data_dir, pattern = "\\.csv$", full.names = TRUE)
if (length(files) == 0) stop("No CSV files found in ", params$data_dir)

raw <- map(files, read_qualtrics) |>
  list_rbind() |>
  distinct(ResponseId, .keep_all = TRUE) |>
  mutate(Duration = as.numeric(`Duration(inseconds)`),
         Progress = as.numeric(Progress),
         Finished = as.logical(toupper(Finished)),
         StartDate = ymd_hms(StartDate, quiet = TRUE))

tibble(file = basename(files)) |> kable(col.names = "Files read")
cat("Rows read (after de-duplication):", nrow(raw), "\n")
```

## Sample and exclusions

Responses are excluded step by step: survey previews / tests, incomplete
responses, failed comprehension checks (if `exclude_failed_checks = TRUE`),
missing advice ratings, and speeders (if `exclude_speeders = TRUE`). Duplicate IP
addresses are flagged.

```{r}
#| label: exclusions

check_amount <- function(x) {
  x <- str_trim(x)
  case_when(x == "1" ~ 0, x == "2" ~ 4, x == "3" ~ 10,
            TRUE ~ suppressWarnings(as.numeric(str_extract(x, "\\d+"))))
}

advice_cols <- str_subset(names(raw), "^advice_.+_\\d+$")

d <- raw |>
  mutate(
    is_preview   = Status %in% c("Survey Preview", "1", "Survey Test", "2") |
                   DistributionChannel %in% c("preview", "test"),
    check_take   = check_amount(Q5) == correct_q5,
    check_give   = check_amount(Q6) == correct_q6,
    checks_pass  = coalesce(check_take & check_give, FALSE),
    has_ratings  = rowSums(!is.na(across(all_of(advice_cols)))) == length(advice_cols),
    dup_ip       = !is.na(IPAddress) & (duplicated(IPAddress) | duplicated(IPAddress, fromLast = TRUE))
  )

med_dur <- median(d$Duration[!d$is_preview & d$Finished], na.rm = TRUE)
d <- d |> mutate(speeder = Duration < params$speeder_cutoff * med_dur)

steps <- list(
  "All recorded responses"                 = rep(TRUE, nrow(d)),
  "Not a preview/test"                     = !d$is_preview,
  "Finished"                               = d$Finished,
  "Passed comprehension checks"            = if (params$exclude_failed_checks) d$checks_pass else rep(TRUE, nrow(d)),
  "All advice ratings present"             = d$has_ratings,
  "Not a speeder"                          = if (params$exclude_speeders) !d$speeder else rep(TRUE, nrow(d))
)
keep <- Reduce(`&`, steps, accumulate = TRUE)
tibble(step = names(steps),
       n_remaining = map_int(keep, sum),
       excluded = c(0, -diff(map_int(keep, sum)))) |>
  kable(col.names = c("Step", "N remaining", "Excluded at this step"))

d_clean <- d[keep[[length(keep)]], ]
N <- nrow(d_clean)
```

**Analysis sample: N = `r N`.**

```{r}
#| label: sample-quality

d_real <- d |> filter(!is_preview, Finished)
tibble(
  Indicator = c("Comprehension check 1 (take £4) correct",
                "Comprehension check 2 (give £0) correct",
                "Both checks correct",
                sprintf("Speeders (< %.0f%% of median duration = %.0f s)",
                        100 * params$speeder_cutoff, params$speeder_cutoff * med_dur),
                "Duplicate IP address"),
  n = c(sum(d_real$check_take, na.rm = TRUE), sum(d_real$check_give, na.rm = TRUE),
        sum(d_real$checks_pass), sum(d_real$speeder, na.rm = TRUE), sum(d_real$dup_ip)),
  pct = round(100 * n / nrow(d_real), 1)
) |> kable(col.names = c("Indicator (non-preview, finished)", "n", "%"))

att <- d_clean |> select(any_of(c("attempts_take", "attempts_give")))
if (ncol(att) && any(!is.na(att))) {
  att |> mutate(across(everything(), as.numeric)) |>
    pivot_longer(everything()) |> count(name, value) |> kable()
} else {
  cat("Note: embedded data 'attempts_take' / 'attempts_give' are empty in this export.\n")
}
```

```{r}
#| label: fig-duration
#| fig-cap: "Completion time (analysis sample). Dashed line = median."
#| fig-height: 3

ggplot(d_clean, aes(Duration / 60)) +
  geom_histogram(binwidth = 0.5, boundary = 0, fill = pal_advice[1], colour = "white") +
  geom_vline(xintercept = median(d_clean$Duration) / 60, linetype = "dashed") +
  labs(x = "Minutes", y = "Participants")

summary(d_clean$Duration / 60) |> round(2)
```

## Reshaping to long format

```{r}
#| label: long

to_score <- function(x) {
  x <- str_trim(x)
  num <- suppressWarnings(as.numeric(x))
  ifelse(!is.na(num), num, match(tolower(x), tolower(likert_levels)))
}

long <- d_clean |>
  select(ResponseId, all_of(advice_cols)) |>
  pivot_longer(-ResponseId, names_to = "var", values_to = "response") |>
  mutate(
    advice_code = str_match(var, "^advice_(.+)_(\\d+)$")[, 2],
    item_code   = str_match(var, "^advice_(.+)_(\\d+)$")[, 3],
    score       = to_score(response),
    advice = coalesce(advice_labels[advice_code], str_to_title(advice_code)),
    advice = factor(advice, levels = unique(c(advice_labels, sort(unique(advice))))),
    advice = droplevels(advice),
    item   = factor(coalesce(item_labels[item_code], paste("Item", item_code)),
                    levels = unique(c(item_labels, paste("Item", sort(unique(item_code)))))),
    item   = droplevels(item),
    response_lbl = factor(likert_levels[score], levels = likert_levels),
    id = factor(ResponseId)
  )

if (any(is.na(long$score))) warning("Some Likert responses could not be converted to numbers.")
pal_adv <- setNames(rep_len(pal_advice, nlevels(long$advice)), levels(long$advice))

head(long |> select(ResponseId, advice, item, response, score), 6)
```

## Descriptive statistics

```{r}
#| label: tbl-desc
#| tbl-cap: "Ratings by advice and item (1 = Strongly disagree, 5 = Strongly agree). % agree = Somewhat/Strongly agree; % disagree = Somewhat/Strongly disagree."

desc <- long |>
  group_by(item, advice) |>
  summarise(n = sum(!is.na(score)),
            mean = mean(score, na.rm = TRUE),
            sd = sd(score, na.rm = TRUE),
            median = median(score, na.rm = TRUE),
            pct_agree = 100 * mean(score >= 4, na.rm = TRUE),
            pct_disagree = 100 * mean(score <= 2, na.rm = TRUE),
            .groups = "drop")
desc |> kable(digits = c(0, 0, 0, 2, 2, 1, 1, 1),
              col.names = c("Item", "Advice", "n", "Mean", "SD", "Median", "% agree", "% disagree"))
```

```{r}
#| label: fig-likert
#| fig-cap: "Distribution of responses. Bars are centred on the neutral category: disagreement to the left, agreement to the right."
#| fig-height: 5.5
#| fig-width: 9

lik <- long |>
  count(item, advice, response_lbl, .drop = FALSE) |>
  group_by(item, advice) |>
  mutate(pct = 100 * n / sum(n)) |>
  ungroup() |>
  mutate(pct_plot = case_when(
    as.integer(response_lbl) < 3  ~ -pct,
    as.integer(response_lbl) == 3 ~ -pct / 2,
    TRUE ~ pct))
neutral_right <- lik |> filter(as.integer(response_lbl) == 3) |> mutate(pct_plot = pct / 2)
lik_plot <- bind_rows(lik, neutral_right)

ggplot(lik_plot, aes(x = pct_plot, y = fct_rev(advice), fill = response_lbl)) +
  geom_col(data = filter(lik_plot, pct_plot < 0),
           position = position_stack(reverse = FALSE), width = 0.7, colour = "white", linewidth = 0.4) +
  geom_col(data = filter(lik_plot, pct_plot >= 0),
           position = position_stack(reverse = TRUE), width = 0.7, colour = "white", linewidth = 0.4) +
  geom_vline(xintercept = 0, colour = "grey40", linewidth = 0.3) +
  facet_wrap(~ item, ncol = 1) +
  scale_fill_manual(values = pal_likert, drop = FALSE, name = NULL,
                    breaks = likert_levels) +
  scale_x_continuous(labels = \(x) paste0(abs(x), "%"), limits = c(-100, 100)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_legend(nrow = 1)) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(colour = "grey90", linewidth = 0.3))
```

```{r}
#| label: fig-means
#| fig-cap: "Mean ratings with 95% within-subject confidence intervals (Cousineau–Morey). Small grey points are individual participants."
#| fig-height: 4
#| fig-width: 9

# Cousineau-Morey within-subject CI
k <- nlevels(long$advice)
ws <- long |>
  group_by(item, id) |> mutate(pmean = mean(score)) |>
  group_by(item) |> mutate(norm = score - pmean + mean(score)) |>
  group_by(item, advice) |>
  summarise(mean = mean(score), n = n(),
            se = sd(norm) / sqrt(n) * sqrt(k / (k - 1)),
            .groups = "drop") |>
  mutate(ci = qt(.975, n - 1) * se)

ggplot(ws, aes(advice, mean, colour = advice)) +
  geom_jitter(data = long, aes(y = score), width = 0.15, height = 0.12,
              colour = "grey75", size = 1, alpha = 0.7) +
  geom_errorbar(aes(ymin = mean - ci, ymax = mean + ci), width = 0.12, linewidth = 0.7) +
  geom_point(size = 3) +
  facet_wrap(~ item) +
  scale_colour_manual(values = pal_adv, guide = "none") +
  scale_y_continuous(breaks = 1:5, limits = c(0.8, 5.2),
                     labels = c("1\nStr. disagree", "2", "3\nNeutral", "4", "5\nStr. agree")) +
  scale_x_discrete(labels = scales::label_wrap(10)) +
  labs(x = NULL, y = "Rating")
```

## Do ratings differ between the advice versions?

The primary tests are non-parametric (ordinal 5-point items); the mixed models
are reported as robustness checks.

### Friedman tests (omnibus, per item)


```{r}
#| label: tbl-friedman

wide_item <- function(it) {
  long |> filter(item == it) |>
    select(id, advice, score) |>
    pivot_wider(names_from = advice, values_from = score) |>
    drop_na()
}

friedman_tbl <- map(levels(long$item), \(it) {
  w <- wide_item(it)
  m <- as.matrix(w[, -1])
  ft <- friedman.test(m)
  tibble(item = it, n = nrow(m), chi2 = unname(ft$statistic), df = unname(ft$parameter),
         p = ft$p.value, kendall_W = unname(ft$statistic) / (nrow(m) * (ncol(m) - 1)))
}) |> list_rbind()

friedman_tbl |> kable(digits = c(0, 0, 2, 0, 3, 3),
                      col.names = c("Item", "n", "χ²", "df", "p", "Kendall's W"))
```

### Pairwise comparisons

Wilcoxon signed-rank tests. *r* = Z/√n
(matched-pairs effect size); *d~z~* = mean difference / SD of differences.
"A > B" / "A < B" counts the participants who rated A higher / lower than B.

```{r}
#| label: tbl-pairwise

pairwise_tbl <- map(levels(long$item), \(it) {
  w <- wide_item(it)
  prs <- combn(levels(long$advice), 2, simplify = FALSE)
  map(prs, \(pr) {
    a <- w[[pr[1]]]; b <- w[[pr[2]]]; dif <- a - b
    wt <- suppressWarnings(wilcox.test(a, b, paired = TRUE, exact = FALSE, correct = TRUE))
    z  <- if (all(dif == 0)) 0 else qnorm(wt$p.value / 2) * -sign(median(dif[dif != 0]))
    tibble(item = it, comparison = paste(pr[1], "vs", pr[2]), n = length(dif),
           mean_diff = mean(dif),
           a_higher = sum(dif > 0), b_higher = sum(dif < 0), ties = sum(dif == 0),
           p = if (all(dif == 0)) 1 else wt$p.value,
           r = z / sqrt(length(dif)),
           dz = if (sd(dif) > 0) mean(dif) / sd(dif) else 0)
  }) |> list_rbind()
}) |> list_rbind() |>
  group_by(item) |> mutate(p_holm = p.adjust(p, "holm")) |> ungroup() |>
  relocate(p_holm, .after = p)

pairwise_tbl |>
  kable(digits = c(0, 0, 0, 2, 0, 0, 0, 3, 3, 2, 2),
        col.names = c("Item", "Comparison", "n", "Mean diff (A−B)", "A > B", "A < B",
                      "Ties", "p", "p (Holm)", "r", "dz"))
```

### Linear mixed model (robustness)

`score ~ advice * item + (1 | participant)`; pairwise contrasts of advice within
each item via `emmeans` (adjusted).

```{r}
#| label: lmm

lmm <- lmer(score ~ advice * item + (1 | id), data = long)
anova(lmm) |> as.data.frame() |> kable(digits = 3)

emm <- emmeans(lmm, ~ advice | item)
pairs(emm, adjust = "tukey") |> as.data.frame() |>
  kable(digits = 3)
```

### Ordinal mixed models (robustness)

Cumulative-link mixed models per item: `score ~ advice + (1 | participant)`.
Coefficients are log-odds of a higher rating relative to the reference advice
(`r levels(long$advice)[1]`). With small samples or little variation these
models may not converge; failures are reported instead of stopping the render.

```{r}
#| label: clmm

clmm_tbl <- map(levels(long$item), \(it) {
  dd <- long |> filter(item == it) |> mutate(y = factor(score, levels = 1:5, ordered = TRUE))
  fit <- tryCatch(ordinal::clmm(y ~ advice + (1 | id), data = dd, nAGQ = 5),
                  error = function(e) e)
  if (inherits(fit, "error")) {
    return(tibble(item = it, term = NA, estimate = NA, se = NA, p = NA,
                  note = paste("Model failed:", conditionMessage(fit))))
  }
  co <- summary(fit)$coefficients
  co <- co[str_detect(rownames(co), "^advice"), , drop = FALSE]
  tibble(item = it, term = str_remove(rownames(co), "^advice"),
         estimate = co[, 1], se = co[, 2], p = co[, 4],
         OR = exp(co[, 1]), note = "")
}) |> list_rbind()

clmm_tbl |> kable(digits = 3)
```

## Participant-level patterns

The three responses give the same recommendation and nearly identical
justifications, so an important pretest question is whether participants
**differentiate** between them at all.

```{r}
#| label: tbl-differentiation

diff_tbl <- long |>
  group_by(item, id) |>
  summarise(identical = n_distinct(score) == 1, range = max(score) - min(score),
            .groups = "drop") |>
  group_by(item) |>
  summarise(`% identical ratings across all versions` = 100 * mean(identical),
            `Mean within-person range` = mean(range),
            .groups = "drop")

all_same <- long |> group_by(id) |>
  summarise(same = all(tapply(score, item, \(x) n_distinct(x) == 1))) |>
  summarise(pct = 100 * mean(same)) |> pull(pct)

diff_tbl |> kable(digits = 1, col.names = c("Item", "% identical ratings across all versions",
                                           "Mean within-person range (points)"))
```

`r round(all_same, 1)`% of participants gave exactly the same ratings to all
versions on **every** item.

```{r}
#| label: tbl-preferred
#| tbl-cap: "Which version does each participant rate highest? Based on the mean of the three items; ties are shown separately."

pref <- long |>
  group_by(id, advice) |> summarise(m = mean(score), .groups = "drop") |>
  group_by(id) |>
  summarise(best = if (sum(m == max(m)) > 1) "Tie" else as.character(advice[which.max(m)]),
            .groups = "drop") |>
  count(best) |> mutate(pct = 100 * n / sum(n)) |>
  arrange(desc(n))
pref |> kable(digits = 1, col.names = c("Highest-rated version", "n", "%"))
```

## Relationships between the items

Spearman correlations between the three items, computed separately for each
advice version. If "standard matters" and "reasoning makes sense" correlate
strongly with "inclined to revise", the first two may act as mechanisms for the
persuasiveness of the advice.

```{r}
#| label: fig-cor
#| fig-height: 3.5
#| fig-width: 9

cors <- long |>
  select(id, advice, item, score) |>
  pivot_wider(names_from = item, values_from = score) |>
  group_by(advice) |>
  group_modify(\(df, key) {
    m <- suppressWarnings(cor(df[, levels(long$item)], method = "spearman", use = "pairwise"))
    as_tibble(m, rownames = "item1") |> pivot_longer(-item1, names_to = "item2", values_to = "rho")
  }) |> ungroup() |>
  mutate(item1 = factor(item1, levels(long$item)), item2 = factor(item2, rev(levels(long$item))))

ggplot(cors, aes(item1, item2, fill = rho)) +
  geom_tile(colour = "white", linewidth = 1) +
  geom_text(aes(label = ifelse(is.na(rho), "–", sprintf("%.2f", rho))), size = 3.5) +
  facet_wrap(~ advice) +
  scale_fill_gradient2(low = "#c73a39", mid = "#f0efec", high = "#2a78d6",
                       limits = c(-1, 1), na.value = "grey95", name = "Spearman ρ") +
  labs(x = NULL, y = NULL) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1), panel.grid = element_blank())
```

## Order effects

The advice blocks were presented in random order (Qualtrics block randomiser
`FL_17`). The order is only in the data if *"Export randomized viewing order"* is
ticked when downloading from Qualtrics (a column like `FL_17_DO`). If present,
this section tests whether the position (1st, 2nd, 3rd) affected the ratings.

```{r}
#| label: order

do_col <- str_subset(names(d_clean), "^FL_\\d+_DO$")
do_col <- do_col[map_lgl(do_col, \(cc) any(str_detect(d_clean[[cc]], paste(names(block_to_advice), collapse = "|")), na.rm = TRUE))]

if (length(do_col) == 0) {
  cat("No display-order column found in this export -> order effects cannot be tested.\n",
      "Tip: in Qualtrics > Data & Analysis > Export, tick 'Export randomized viewing order'.\n")
} else {
  ord <- d_clean |>
    select(ResponseId, order = all_of(do_col[1])) |>
    mutate(order = str_split(order, "\\|")) |>
    unnest_longer(order, indices_to = "position") |>
    mutate(advice_code = block_to_advice[str_trim(order)]) |>
    filter(!is.na(advice_code))
  long_ord <- long |> left_join(ord |> select(ResponseId, advice_code, position),
                                by = c("ResponseId", "advice_code"))
  long_ord |> group_by(item, position) |>
    summarise(mean = mean(score), sd = sd(score), n = n(), .groups = "drop") |>
    kable(digits = 2) |> print()
  lmm_ord <- lmer(score ~ advice * item + factor(position) + (1 | id), data = long_ord)
  anova(lmm_ord) |> as.data.frame() |> kable(digits = 3) |> print()
}
```

## Planning the main study

Observed paired effect sizes (*d~z~*) from the pretest and the number of
participants a **within-subject** paired *t*-test would need for 80% power
(α = .05, two-sided) to detect them. Pretest effect sizes are imprecise with small
samples; treat these as rough guidance only.

```{r}
#| label: tbl-power

power_tbl <- pairwise_tbl |>
  select(item, comparison, dz) |>
  mutate(N_needed_80 = map_dbl(dz, \(e) {
    if (is.na(e) || abs(e) < 0.02) return(NA_real_)
    ceiling(power.t.test(delta = abs(e), sd = 1, sig.level = .05, power = .80,
                         type = "paired")$n)
  }))
power_tbl |> kable(digits = 2, col.names = c("Item", "Comparison", "Observed dz", "N for 80% power"))
```

## Summary of key numbers

```{r}
#| label: summary

best <- desc |> group_by(item) |> slice_max(mean, n = 1, with_ties = TRUE) |>
  summarise(top = paste(advice, collapse = " / "), mean = first(mean), .groups = "drop")

tibble(
  Item = friedman_tbl$item,
  `Highest mean` = best$top[match(friedman_tbl$item, best$item)],
  `Friedman p` = friedman_tbl$p,
  `Kendall's W` = friedman_tbl$kendall_W,
  `Significant pairs (Holm p < .05)` = map_chr(friedman_tbl$item, \(it) {
    s <- pairwise_tbl |> filter(item == it, p_holm < .05)
    if (nrow(s) == 0) "none" else paste(s$comparison, collapse = "; ")
  })
) |> kable(digits = 3)
```

```{r}
#| label: save
#| include: false

if (params$save_outputs) {
  write_csv(d_clean |> select(-any_of(c("IPAddress", "LocationLatitude", "LocationLongitude"))),
            "output/pretest_clean_wide.csv")
  write_csv(long |> select(ResponseId, advice, item, response, score),
            "output/pretest_clean_long.csv")
  write_csv(desc, "output/pretest_descriptives.csv")
  write_csv(friedman_tbl, "output/pretest_friedman.csv")
  write_csv(pairwise_tbl, "output/pretest_pairwise.csv")
}
```

::: {.callout-note}
## Notes

- Cleaned files are written to `output/` next to this document (IP addresses and
  locations are removed). The raw Qualtrics exports are never modified.
- For the order-effects analysis, export the data with *"Export randomized viewing order"* ticked.
- If `attempts_take` / `attempts_give` should record comprehension attempts, check the
  embedded-data setup in Qualtrics – they are currently exported empty.
:::

```{r}
#| label: session
#| code-fold: true
#| results: hold

sessionInfo()
```
